Plots and tables summarizing results of Poisson simulations

### 2019-11-14 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

Load the knitr, kableExtra, ggplot2 and cowplot packages.

```{r load-pkgs, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
library(cowplot)
```

@@

*Create plot showing combined results here.*

>>>>

Load the plyr, knitr, kableExtra, ggplot2 and cowplot packages.

```{r load-pkgs, message=FALSE, warning=FALSE}
library(plyr)
library(knitr)
library(kableExtra)
library(ggplot2)
library(cowplot)
```

@@

These plots summarize the results for all 6 simulation scenarios.

```{r summarize-all-results, fig.height=6, fig.width=10}
pdat.s1$simulation   <- "Spikes"
pdat.s8$simulation   <- "Spikes"
pdat.s128$simulation <- "Spikes"
pdat.s1$intensity    <- "(1/100, 3)"
pdat.s8$intensity    <- "(1/8, 8)"
pdat.s128$intensity  <- "(1/128, 128)"

pdat.ang1$simulation   <- "Angles"
pdat.ang8$simulation   <- "Angles"
pdat.ang128$simulation <- "Angles"
pdat.ang1$intensity    <- "(1/100, 3)"
pdat.ang8$intensity    <- "(1/8, 8)"
pdat.ang128$intensity  <- "(1/128, 128)"

pdat.hs1$simulation   <- "Heavisine"
pdat.hs8$simulation   <- "Heavisine"
pdat.hs128$simulation <- "Heavisine"
pdat.hs1$intensity    <- "(1/100, 3)"
pdat.hs8$intensity    <- "(1/8, 8)"
pdat.hs128$intensity  <- "(1/128, 128)"

pdat.bur1$simulation   <- "Bursts"
pdat.bur8$simulation   <- "Bursts"
pdat.bur128$simulation <- "Bursts"
pdat.bur1$intensity    <- "(1/100, 3)"
pdat.bur8$intensity    <- "(1/8, 8)"
pdat.bur128$intensity  <- "(1/128, 128)"

pdat.cb1$simulation   <- "Clipped"
pdat.cb8$simulation   <- "Clipped"
pdat.cb128$simulation <- "Clipped"
pdat.cb1$intensity    <- "(1/100, 3)"
pdat.cb8$intensity    <- "(1/8, 8)"
pdat.cb128$intensity  <- "(1/128, 128)"

pdat.b1$simulation   <- "Bumps"
pdat.b8$simulation   <- "Bumps"
pdat.b128$simulation <- "Bumps"
pdat.b1$intensity    <- "(1/100, 3)"
pdat.b8$intensity    <- "(1/8, 8)"
pdat.b128$intensity  <- "(1/128, 128)"

pdat <- rbind(pdat.s1,pdat.s8,pdat.s128,
              pdat.ang1,pdat.ang8,pdat.ang128,
              pdat.hs1,pdat.hs8,pdat.hs128,
              pdat.bur1,pdat.bur8,pdat.bur128,
              pdat.cb1,pdat.cb8,pdat.cb128)
p1   <- create.bar.plots(pdat,show.legend = FALSE)
pdat <- rbind(pdat.b1,pdat.b8,pdat.b128)
p2   <- create.bar.plots(pdat)
plot_grid(p1,p2,nrow = 1,rel_widths =  c(7,4))
```
